A non-additive generalization of probability theory\\for quantum mechanics and beyond

### 2025-07-02 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex
Add Kolmogorov axioms

\usepackage{assumptionsofphysics}
\usepackage{tikz}
\usepackage{breakurl}
\usepackage{tcolorbox}

@@

Another way to represent quantum ensembles is through the use of quasiprobability distributions. Given a topological space $X$, a measure $\mu: \mathcal{B}(X) \to \mathbb{R}$ is affine if $\mu(X)=1$, where $\mathcal{B}(X)$ is the Borel $\sigma$-algebra. All probability measures are affine measures, but the reverse is not true, as affine measures can be negative on particular regions. The Wigner function, for example, can be negative over small regions of phase space.

>>>>

\usepackage{assumptionsofphysics}
\usepackage{tikz}
\usepackage{breakurl}
\usepackage{tcolorbox}
\usepackage{scrextend}	% for environment ``labeling''

@@

Another way to represent quantum ensembles is through the use of quasiprobability distributions. These distributions (or measures) relax some of Kolmogorov's probability axioms\footnote{TODO: These should be stated earlier.}.

A measure $\mu: \Omega_X \to \mathbb{R}$ over a sample space $X$ with $\sigma$-algebra $\Omega_X$ is called a probability measure if it satisfies the following three axioms
\begin{labeling}{Non-negativity:}
	\item[Non-negativity:] $\forall x \in \Omega_X: \mu(x) \ge 0$
	\item[Normalization:] $\mu(X) = 1$
	\item[$\sigma$-additivity:] $\mu ( \bigcup_i x_i ) = \sum_i \mu ( x_i )$ for any countable sequence of disjoint sets $x_i \in \Omega_X$.
\end{labeling}

For example, affine measures do not necessarily satisfy non-negativity. The Wigner function is the probability density of such a measure and can be negative over small regions of phase space.
